Pillar 1 - Sequential Pattern Mining

### 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
simplify code

# Number of students
n_students <- d_transactions %>%
  select(sequenceID) %>%
  n_distinct()

# Probability of taken a course
d_support_take <- d_transactions %>%
  distinct(
    item,
    sequenceID
    ) %>%
  group_by(
    item
    ) %>%
  summarise(
    count     = n(),
    rate.take = count / n_students,
    rate.not  = 1 - rate.take
    )

>>>>

# Number of students
n_students <- d_transactions %>%
  select(sequenceID) %>%
  n_distinct

# Probability of taking a course
d_support_take <- d_transactions %>%
  distinct(
    item,
    sequenceID
    ) %>%
  count(
    item
    ) %>%
  mutate(
    rate.take = n / n_students,
    rate.not  = 1 - rate.take)
